### 2024-03-24 src/data_prep/data_prep.Rmd
added image saving

```{r reformatting the data, message=FALSE, warning=FALSE, include=FALSE}
movie_data <- read_csv("data/movie_data.csv")

@@

The mean of the averageRating variable is 6.6.

```{r DV scale, echo=FALSE}
Okay. So the scale is okay BUT remember that these are AVERAGE ratings, and that on average ratings 1 and 10 are quite extreme and frankly, unrealistic.

let's visualize how ratings are distributed

```{r DV plots, echo=FALSE, message=FALSE, warning=FALSE}
ggplot((movie_data), aes(x = averageRating)) +
  geom_histogram(binwidth = 1, fill = "darkorange", color = "black") +
  labs(title = "Distribution of averageRating",
       x = "Average Rating",y = "Frequency") +
  scale_x_continuous(breaks = seq(0, 10, by = 1)) +  
  theme_minimal()
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(movie_data, aes(x = averageRating)) +
  geom_histogram(binwidth = 0.1, fill = "orange", color = "black") +
  scale_x_continuous(breaks = seq(0, 10, by = 0.5), limits = c(0, 10), labels = scales::number_format(accuracy = 0.1)) +
  labs(x = "averageRating", y = "Frequency") +
  theme_minimal()
```

@@

```{r Plot DV and numVotes, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(movie_data, aes(x = numVotes)) +
  geom_dotplot(fill = "darkorange", color = "black", binwidth = 500) +
  labs(title = "Distribution of numVotes",
       x = "Number of Votes", y = "Frequency") + 
  theme_minimal()

movie_data$numVotes_group <- cut(movie_data$numVotes, breaks = c(-Inf, 50, Inf), labels = c("Below 50", "Above 50"))
print(table(movie_data$numVotes_group))
```

@@

ggplot(below_100, aes(x = numVotes)) +
  geom_histogram() +
  labs(title = "Distribution of numVotes Below 100",
       x = "Group (Interval of 10)", y = "Number of Votes") +
  theme_minimal()
```

@@

movie_data %>%
  group_by(slide_window_5) %>%
  count()
```
We have filtered the data set to only include movies and series that have been released after 1925.

@@

```{r include=FALSE}
movie_data <- movie_data %>%
  mutate(genres = tolower(genres)) %>%
  separate_rows(genres, sep = ",") %>%
  mutate(genres = as.factor(genres))
```

@@

```{r echo=FALSE}
ggplot(movie_data, aes(x = numVotes, y = averageRating, color= genres)) +
  geom_point() + 
  facet_wrap(~genres)
```

@@

Let's see how the actual ratings are then distributed across genres
```{r echo=FALSE}
ggplot(movie_data, aes(averageRating, color= genres))+
  geom_bar() +
  facet_wrap(~genres)
```

@@

```{r echo=FALSE}
ggplot(movie_data, aes(sample = averageRating, color = genres)) +
  stat_qq() +
  facet_wrap(~genres)
```

@@

# Plot residuals versus fitted values
ggplot(plot_data, aes(x = Fitted_Values, y = Residuals)) +
  geom_point() +
  geom_smooth(method = "loess", se = FALSE) + 
  labs(x = "Fitted Values", y = "Residuals") +  
  ggtitle("Residuals vs. Fitted Values")  
```

@@

# Plot residuals versus index
ggplot(plot_data, aes(x = Index, y = Residuals)) +
  geom_point() +
  geom_smooth(method = "loess", se = FALSE) +  
  labs(x = "Index", y = "Residuals") +  
  ggtitle("Residuals vs. Index")
```

@@

```{r echo=FALSE}
ggplot(movie_data, aes(x = slide_window_5, y = averageRating)) +
  geom_point() +
  facet_wrap(~genres)
```

>>>>

```{r reformatting the data, message=FALSE, warning=FALSE, include=FALSE}
movie_data <- read_csv("movie_data.csv")

@@

The mean of the averageRating variable is 6.6. 
Okay. So the scale is okay BUT remember that these are AVERAGE ratings, and that on average ratings 1 and 10 are quite extreme and frankly, unrealistic. let's visualize how ratings are distributed

```{r DV plots, echo=FALSE, message=FALSE, warning=FALSE}
distribution_of_average_ratings <- ggplot((movie_data), aes(x = averageRating)) +
  geom_histogram(binwidth = 1, fill = "darkorange", color = "black") +
  labs(title = "Distribution of averageRating",
       x = "Average Rating",y = "Frequency") +
  scale_x_continuous(breaks = seq(0, 10, by = 1)) +  
  theme_minimal()

ggsave("../../gen/data_preparation/distribution_of_average_ratings.png", distribution_of_average_ratings)

distribution_of_average_ratings
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
distribution_of_average_ratings_unrounded <- ggplot(movie_data, aes(x = averageRating)) +
  geom_histogram(binwidth = 0.1, fill = "orange", color = "black") +
  scale_x_continuous(breaks = seq(0, 10, by = 0.5), limits = c(0, 10), labels = scales::number_format(accuracy = 0.1)) +
  labs(x = "averageRating", y = "Frequency") +
  theme_minimal()

ggsave("../../gen/data_preparation/distribution_of_average_ratings_unrounded.png", distribution_of_average_ratings_unrounded)

distribution_of_average_ratings_unrounded
```

@@

```{r Plot DV and numVotes, echo=FALSE, message=FALSE, warning=FALSE}
distribution_of_number_of_votes <- ggplot(movie_data, aes(x = numVotes)) +
  geom_dotplot(fill = "darkorange", color = "black", binwidth = 500) +
  labs(title = "Distribution of numVotes",
       x = "Number of Votes", y = "Frequency") + 
  theme_minimal()

movie_data$numVotes_group <- cut(movie_data$numVotes, breaks = c(-Inf, 50, Inf), labels = c("Below 50", "Above 50"))
print(table(movie_data$numVotes_group))

ggsave("../../gen/data_preparation/distribution_of_number_of_votes.png", distribution_of_number_of_votes)

distribution_of_number_of_votes
```

@@

distribution_of_number_of_votes_below_10 <-  ggplot(below_100, aes(x = numVotes)) +
  geom_histogram() +
  labs(title = "Distribution of numVotes Below 100",
       x = "Group (Interval of 10)", y = "Number of Votes") +
  theme_minimal()

ggsave("../../gen/data_preparation/distribution_of_number_of_votes_below_10.png", distribution_of_number_of_votes_below_10)

distribution_of_number_of_votes_below_10
```

@@

movie_data %>%
  group_by(slide_window_5) %>%
  count()

```
We have filtered the data set to only include movies and series that have been released after 1925.

@@

```{r include=FALSE}
movie_data <- movie_data %>%
  mutate(genres = tolower(genres)) %>%
  separate_rows(genres, sep = ",") %>%
  mutate(genres = as.factor(genres))

```

@@

```{r echo=FALSE}
number_of_votes_vs_average_rating <- ggplot(movie_data, aes(x = numVotes, y = averageRating, color= genres)) +
  geom_point() + 
  facet_wrap(~genres)

ggsave("../../gen/data_preparation/number_of_votes_vs_average_rating.png", number_of_votes_vs_average_rating)

number_of_votes_vs_average_rating
```

@@

Let's see how the actual ratings are then distributed across genres
```{r echo=FALSE}
number_of_votes_distributions_per_genre <- ggplot(movie_data, aes(averageRating, color= genres))+
  geom_bar() +
  facet_wrap(~genres)

ggsave("../../gen/data_preparation/number_of_votes_distributions_per_genre.png", number_of_votes_distributions_per_genre)

number_of_votes_distributions_per_genre
```

@@

```{r echo=FALSE}
qq_normality <- ggplot(movie_data, aes(sample = averageRating, color = genres)) +
  stat_qq() +
  facet_wrap(~genres)

ggsave("../../gen/data_preparation/qq_normality.png", qq_normality)

qq_normality
```

@@

# Plot residuals versus fitted values
homoskedacity <- ggplot(plot_data, aes(x = Fitted_Values, y = Residuals)) +
  geom_point() +
  geom_smooth(method = "loess", se = FALSE) + 
  labs(x = "Fitted Values", y = "Residuals") +  
  ggtitle("Residuals vs. Fitted Values")

ggsave("../../gen/data_preparation/homoskedacity.png", homoskedacity)

homoskedacity

```

@@

# Plot residuals versus index
independence <- ggplot(plot_data, aes(x = Index, y = Residuals)) +
  geom_point() +
  geom_smooth(method = "loess", se = FALSE) +  
  labs(x = "Index", y = "Residuals") +  
  ggtitle("Residuals vs. Index")

ggsave("../../gen/data_preparation/independence.png", independence)

independence

```

@@

```{r echo=FALSE}
linearity <- ggplot(movie_data, aes(x = slide_window_5, y = averageRating)) +
  geom_point() +
  facet_wrap(~genres)

ggsave("../../gen/data_preparation/linearity.png", linearity)

linearity
```
